On the Construction of a Collision-Free Schedule of Beacons in a Wireless Multi-Hop Network

### 2013-10-09 paper.tex
more previous work

\section{Related Work}
An initial step in the direction we are exploring in this later was taken in \cite{cano2013iri}.
In that paper, the construction of a collision-free schedule is studied for a sensor network.
That paper focused on a simple scenario in which all nodes could hear each other transmissions.
Another difference between that paper and the present letter is that here we not aim to compute a schedule length which is similar or equal to the participating nodes.
In the present letter the schedule is independently computed by each node and therefore it is possible that different nodes use different schedule lengths.

>>>>

\section{Related Work}
A first attempt of a collision-free MAC protocol for multi-hop wireless networks appeared in \cite{barcelo2013dcc}.
That solution does not use beacons, and therefore the convergence is slower and the efficiency is lower.

An initial step in the direction we are exploring in this later was taken in \cite{cano2013iri}.
In that paper, the construction of a collision-free schedule is studied for a sensor network.
That paper focused on a simple scenario in which all nodes could hear each other transmissions.
Another difference between that paper and the present letter is that here we not aim to compute a schedule length which is similar or equal to the participating nodes.
In the present letter the schedule is independently computed by each node and therefore it is possible that different nodes use different schedule lengths.
